---
title: "Importing Spatial Data"
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float:
      collapsed: false
      smooth_scroll: false
---

<style>
.title{
  display: none;
}
body {
  text-align: justify
}
.center {
  display: block;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{css, echo=FALSE}
.watch-out {
  color: black;
}
```

```{r setup, include=FALSE}
# use rmarkdown::render_site(envir = knitr::knit_global())
knitr::opts_chunk$set(highlight = TRUE, echo = TRUE)
```

<br>

VoltRon includes built-in functions for converting readouts from a large selection of spatial omic instruments into R objects. In this tutorial, we will review each built-in function that is geared towards importing readouts of a specific spatial omic technology. 

# Importing Spatial Datasets

## Xenium

```{r eval = FALSE, class.source="watch-out"}
library(VoltRon)
Xen_R1 <- importXenium("Xenium_R1/outs", sample_name = "XeniumR1")
```

```
VoltRon Object 
XeniumR1: 
  Layers: Section1 
Assays: Xenium(Main) 
```

</br>

```{r eval = FALSE, class.source="watch-out"}
library(VoltRon)
Xen_R1 <- importXenium("Xenium_R1/outs", sample_name = "XeniumR1", import_molecules = TRUE)
```

```
VoltRon Object 
XeniumR1: 
  Layers: Section1 
Assays: Xenium(Main) Xenium_mol 
```

</br>
