---
title: "ondisk"
output: 
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
---

<style>
.title{
  display: none;
}
body {
  text-align: justify
}
.center {
  display: block;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{css, echo=FALSE}
.watch-out {
  color: black;
}
```

```{r setup, include=FALSE}
# use rmarkdown::render_site(envir = knitr::knit_global())
knitr::opts_chunk$set(highlight = TRUE, echo = TRUE)
```

<br>

# OnDisk Storage

**VoltRon** includes interactive applications to select and manually label spatial points by drawing polygons and circles. As an example, we will use a Spot-based spatial transcriptomic assay, specifically the **Mouse Brain Serial Section 1/2** datasets, analyzed in the [Niche Clustering](deconvolution.html) tutorial. You can find the already analyzed data stored as a VoltRon object [here](https://bimsbstatic.mdc-berlin.de/landthaler/VoltRon/NicheClustering/Visium&Visium_data_decon_analyzed.rds)

```{r class.source="watch-out", eval = FALSE}
MBrain_Sec <- readRDS("Visium&Visium_data_decon_analyzed.rds")
```